\documentclass{article}
\usepackage[top=1.25in, bottom=1.25in, left=1.25in, right=1.25in]{geometry}
\usepackage{amsmath, amsthm, amssymb}
\begin{document}
\begin{center} Thesis Outline \end{center}
\begin{enumerate}

\item Introduction \begin{enumerate}
    \item Define Coxeter system, braid relation, commutation, bond strength, Coxeter graph, types ($A_n \cong S_{n+1}$ via $s_i \mapsto (i \ i+1)$); examples.
    \item Define word, reduced expression, length, Coxeter element, fully commutative, cyclically reduced, cyclically equivalent, commutation equivalent, cyclically fully commutative, heaps; examples.
    \item FC if and only if no reduced expression has braid relations, observation; example.
    \item Matsumoto's theorem, observation; example.
    \item Heap correspondence with commutation classes, FCC if and only if unique heap; example.
    \item Define kappa-equivalence; example.
    \item Cyclic version of Matsumoto's theorem; example.
    \item Erikssons' theorem, observation; example.
    \item Reduced expressions box in $A_4$.
    \item Note that some of these results are analogous to known results in the symmetric group, but we put them in the Coxeter context.
\end{enumerate}

\item CFC elements in $A_n$ \begin{enumerate}
	\item Define CFC in $A_n$, weak and strong block types; examples.
	\item Switch between heaps and cycles.
	\item Pattern avoidance with diagrams; examples.
	\item String diagrams (crossings, choice of crossing implies more than one heap), heaps; examples.
	\item Example using string diagram, heap, cycle, one line to show CFC, FC, not FC.
	\item Note that cycle type does not generalize to types other than $A_n$; same block type implies same cycle type implies conjugate.
\end{enumerate}

\item Conjugacy classes of CFC elements in $A_n$ \begin{enumerate}
	\item Lemma -- CFC is cyclically equivalent to diagonal block type $(k)$, proof; example.
	\item Define squeeze operation; example.
	\item Lemma -- $m(s,t) = 3$ implies $stst = ts$ (heaps).
	\item Lemma -- translate left and right, proof; example (show exactly by which element you have to conjugate).
	\item Define boomerang operation; example.
	\item Lemma -- switch between block type $(k,m)$ to $(m,k)$, proof; example (show exactly by which element you have to conjugate; to switch back, conjugate by the inverse).
	\item Examples.
	\item If $w \in \text{CFC}(W)$, is $xwx^{-1} \in \text{CFC}(W)$ not on the list? No. Take the ``simple" (diagonal, tight) CFC heap of the corresponding block type, then translate and swap.
\end{enumerate}

\item Connection to cycles

\item Open questions

\end{enumerate}
\end{document}